Emergent dual scaling of riverine biodiversity

### 2021-03-26 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

The present study combines theory and analysis of extensive community data from two different regions of the globe to show that multiple ecological pathways converge to the emergence of dual diversity scaling. Specifically, watershed-scale species richness ($\gamma$ diversity) increased linearly with ecosystem size $A$ and branching probability $P_b$ on logarithmic axes as $log_{10}~\gamma = log_{10}~c + \xi_1 log_{10}~A + \xi_2log_{10}~P_b$ ($\xi_1$ and $\xi_2$ are the scaling exponents) regardless of ecological contexts. However, contributing factors of increased $\gamma$ diversity - either enhanced local species richness ($\alpha$ diversity) and/or spatial variation of species composition ($\beta$ diversity) - depended on constituent species' characteristics. Our findings suggest that the dual scaling law is a pervasive yet overlooked feature of complex ecosystems with important implications for biodiversity conservation.

>>>>

The present study combines theory and analysis of extensive community data from two different regions of the globe to show that multiple ecological pathways converge to the emergence of dual diversity scaling. Specifically, watershed-scale species richness ($\gamma$ diversity) followed power laws with ecosystem size $A$ and branching probability $P_b$ as $\gamma = cA^{\xi_1}P_b^{\xi_2}$ ($\xi_1$ and $\xi_2$ are the scaling exponents) regardless of ecological contexts. However, contributing factors of increased $\gamma$ diversity - either enhanced local species richness ($\alpha$ diversity) and/or spatial variation of species composition ($\beta$ diversity) - depended on constituent species' characteristics. Our findings suggest that the dual scaling law is a pervasive yet overlooked feature of complex ecosystems with important implications for biodiversity conservation.
